Maintenance planning on French military aircraft operations

### 2018-03-01 R/OptiPlan_presentation/proposal.Rmd
New version of Optiplan document. Added resources for document: img, diagrams in R

# Optiplan proposal

@@

<!-- TODO: translate into non-mathematical -->

The problem is considered a Flight and Maintenance Planning problem. Work has been already done by \citet{Kozanidis2008}, \citet{Cho2011}, \citet{Verhoeff2015} and \citet{Chastellux2016}, among others.

@@

### Proposal

@@

![](../../img/functionalities.png)

@@

![](../../img/cases.png)

@@

Here, an interactive gantt is used to present and potentially modify a maintenance plan:

<!-- TODO: gantt example -->

Here, an interactive graph is used to present the usage of aircraft:

<!-- TODO: rut example -->

Here, an interactive table is used to present the usage of aircraft:

<!-- TODO: DT example -->

@@

![Proposed architecture with data flows between components](../../img/architecture.png)

@@

>>>>

---
title: "Optiplan proposal"
date: "March 11, 2018"
output: 
  html_document:
    css: ./../../css/baobab_docs.css
    toc: true
  beamer_presentation:
    theme: "Berlin"
    toc: true
    slide_level: 3
    incremental: yes
    fig_height: 4
    # footer: "ISAE-SUPAERO, Université de Toulouse, France"
    includes:
        in_header: header.tex
  slidy_presentation:
    css: ./../../css/baobab_MH.css
    incremental: yes
    footer: "ISAE-SUPAERO, Université de Toulouse, France"
    slide_level: 4
    toc: true
nocite: '@*'
bibliography: MFMP.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
setwd("../")
source('scripts/params.R')
source('scripts/import_results.R')
source('diagrams/cases.R')
source("diagrams/architecture.R")
source("diagrams/functionalities.R")
source('diagrams/exampleDT.R')
exp_directory = PATHS[['experiments']] %>% paste0('201802141539/')
gantt <- print_solution(exp_directory, max_resources = 5, width="100%", height="200px")
graphs_rem <- graph_remaining(exp_directory)
table_rem <- table_remaining(exp_directory)
html_output <- knitr::opts_knit$get("rmarkdown.pandoc.to") %in% c("slidy", 'html')
```

@@

The problem is considered a Flight and Maintenance Planning problem. Work has been already done by @Kozanidis2008, @Cho2011, @Verhoeff2015 and @Chastellux2016, among others.

@@

## Proposal

@@

```{r, echo=FALSE, out.width='70%'}
if (html_output){
    graph_functionalities()
} else {
    knitr::include_graphics('../../img/functionalities.png')
}
```

@@

```{r, echo=FALSE, out.width='70%'}
if (html_output){
    graph_cases()
} else {
    knitr::include_graphics('../../img/cases.png')
}
```

@@

Here, an interactive gantt is used to present and potentially modify a maintenance plan. It is possible to edit the maintenances and assignments tasks (change the size or move it) by double clicking on them and dragging. Also, it is possible to add new assignments by double clicking.

```{r, echo=FALSE, out.width='70%'}

if (html_output){
    gantt
} else {
    knitr::include_graphics('./../../img/calendar.png')
}
```

Here, an interactive graph is used to present the evolution of the status of a single aircraft over time:

```{r, echo=FALSE, out.width='90%'}

if (html_output){
    graphs_rem
} else {
    knitr::include_graphics('./../../img/remaining.png')
}
```

Here, an interactive table is used to present some data:

```{r, echo=FALSE, out.width='90%'}

if (html_output){
    table_rem
}
```

@@

```{r, echo=FALSE, out.width='70%'}

if (html_output){
    graph_architecture()
} else {
    knitr::include_graphics('../../img/architecture.png')
}
```

<!-- ![Proposed architecture with data flows between components]() -->

@@

### References

### 2018-03-01 R/roadef_presentation/roadef_presentation.Rmd
New version of Optiplan document. Added resources for document: img, diagrams in R

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
setwd("../")
source('scripts/params.R')
source('scripts/import_results.R')
# library(png)
# library(grid)
exp_directory = PATHS[['experiments']] %>% paste0('201802141539/')
gantt <- print_solution(exp_directory, max_resources = 30)
show_gantt <- knitr::opts_knit$get("rmarkdown.pandoc.to")=="slidy"
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
setwd("../")
source('scripts/params.R')
source('scripts/import_results.R')
exp_directory = PATHS[['experiments']] %>% paste0('201802141539/')
gantt <- print_solution(exp_directory, max_resources = 30)
show_gantt <- knitr::opts_knit$get("rmarkdown.pandoc.to")=="slidy"
```
